Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-11 manuscript.Rnw
add in Bechtel and Scheve example; update figures; edit

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
%\usepackage{times}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}

\title{Measuring Subgroup Preferences in Conjoint Experiments}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}

@@

{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences. The method powerfully disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies. Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features. While the AMCE has a clear causal interpretation, most published conjoint analyses also use AMCEs to simply describe preferences, often including comparisons of AMCEs between subgroups of respondents. We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple, but often forgotten, property that interactions are sensitive to the reference category used in regression analysis. This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance. We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test. Given the rapidly accelerating use of conjoint analyses, this paper makes an important contribution by highlighting pitfalls and presenting advice for best practice in the analysis and presentation of conjoint experiments.}

@@

<<setup, cache=FALSE>>=
library("rio")
library("cregg")
library("ggplot2")
requireNamespace("xtable", quietly = TRUE)
@

@@

## covariates
hainmueller_immigration$ethnocentrism_split <- ifelse(is.na(hainmueller_immigration$ethnocentrism), NA_real_, ifelse(hainmueller_immigration$ethnocentrism > 10, 1, 0))
hainmueller_immigration$ethnocentrism_split <- factor(hainmueller_immigration$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
@

@@

@@

Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science. While traditional survey experiments tend to examine just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}. The driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE). By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline, averaging across all respondents and all other profile features.

While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs for \textit{descriptive} purposes: that is, to map variation in favorability toward a multidimensional object across its various features. This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity. For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups. Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income. In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations. \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents. \citet{KirklandCoppock2017} do a similar comparison between Democrats and Republicans in hypothetical elections.

In these and many other articles, interpretation of these subgroup analyses focus not just on the \textit{causal effects} of profile features within each subgroup (what Hainmueller et al. term ``conditional AMCEs''; 13) but also on an implied quantity of interest: the \textit{difference} between two conditional AMCEs across subgroups. Searching for causal effect heterogeneity is an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017}, yet most conjoint analyses use this difference-in-AMCEs instead to \textit{descriptively} interpret apparent differences in favorability toward objects with a given feature (e.g., immigrants from Syria) between the two groups (e.g., low and high ethnocentrism respondents).

What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in differences-in-AMCEs. Yet authors frequently use visual or more formal comparisons of conditional AMCEs to make descriptive claims about such differences, leading themselves and readers astray. Differences in AMCEs do not provide inference into difference between subgroups' favorability toward a conjoint feature. In this paper, we show that a difference in underlying subgroup preferences --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs under particular preference configurations and analytic choices. The underlying cause of this error is simple and familiar to any applied researcher but appears to be forgotten in most applied conjoint work.

As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability. Yet most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment. Ultimately AMCEs are relative, not absolute, statements about preferences so subgroup differences are also relative not absolute statements about preference heterogeneity.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} There is simply no predictable inference to be drawn from subgroup causal effects to the levels of underlying subgroup opinion. This inferential error --- interpreting differences in the size of causal effects as descriptive differences in preferences --- appears to be widespread in published conjoint analyses. The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors. \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between features of conjoint profiles. The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.

In what follows, we demonstrate the challenges of conjoint analysis and reminder readers of how reference category choice for profile features creates significant problems for comparing conditional AMCEs across respondent subgroups. We show how the use of an arbitrary reference category means the size and the direction of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features and that reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar, using examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BallardRosaMartinScheve2016, TeeleKallaRosenbluth2018}). The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (1) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein. Newly developed software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout. We conclude with advice for best practices in the analysis and presentation of conjoint results.

@@

Conjoint analysis serves two purposes. One is to assess causal effects. Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design. Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features. Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.

Importantly, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved). All quantities of interest relevant to the analysis of conjoint designs derive from combinations of cell means, marginal means, and the grand mean, as is common in the traditional analysis of factorial experiments. In a forced choice design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen). \textit{Cell means} are the mean outcome for each particular combination of feature levels. In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved. For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved. While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions. Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.

Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features. A marginal mean describes the level of favorability toward profiles that have a particular feature level, marginalizing across all other features. For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $Pr(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $(Pr(Y=1|X=x)=1$.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany). Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability. If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$. If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one. This constraint on the range of the marginal means also constrains the range of AMCEs. Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018}. In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex. Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.

<<hainmueller_candidate_replication, dependson=c("data_hainmueller_candidate"), fig.height=6, fig.width=8, fig.cap="Replication of Hainmueller et al. (2014) Candidate Experiment using AMCEs and MMs", fig.show="hold", message=FALSE>>=
plot(
  cregg::cj(
   hainmueller_candidate, 
   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
   id = ~ resID,
   estimate = "amce"
  ), vline = 0, xlim = c(-0.4,0.4)
)
plot(
  cregg::cj(
   hainmueller_candidate, 
   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
   id = ~ resID,
   estimate = "mm"
  ), vline = 0.5, xlim = c(0.25,0.75)
)
@

Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation. For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category. This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform. We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of the Hainmueller et al. candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel). Here and throughout we use visual presentation of results, but full numerical estimates including appropriate standard errors are presented in the Appendix. Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined). For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively.

The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature; for example, ``male candidates are preferred to female candidates'' \citep[6]{TeeleKallaRosenbluth2018}. \citet{HainmuellerHopkinsYamamoto2014} similarly describe some of the results of conjoint on preferences toward Congressional candidates:

@@

The most basic thing that can be learned about the distribution of $Y$ is the expected value, $E[Y]$, or \textit{grand mean} (in the parlance of factorial experiments). We can think of this quantity in terms of the survey implementation process (namely, respondents, tasks, and profiles) or as a simple function of the resulting data:

@@

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
%\usepackage{times}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}

\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}

@@

{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences. The method powerfully disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies. Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features. While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to simply describe \textit{levels} of preferences or favorability, often including comparisons of AMCEs between subgroups of respondents. We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple property that regression interactions are sensitive to the reference category used in the analysis. This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance. We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test. Amidst the rapidly accelerating use of conjoint analyses, we highlight common pitfalls and offer advice for best practice in the analysis and presentation of conjoint experiments.}

@@

<<setup, cache=FALSE>>=
library("rio")
library("cregg")
library("ggplot2")
library("gridExtra")
requireNamespace("xtable", quietly = TRUE)
@

@@

## covariates
hainmueller_immigration$ethnocentrism_split <- ifelse(is.na(hainmueller_immigration$ethnocentrism), NA_real_, ifelse(hainmueller_immigration$ethnocentrism > 10, 1, 0))
hainmueller_immigration$ethnocentrism_split <- factor(hainmueller_immigration$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))

## constraints
hainmueller_immigration$constraint1constrained <- ifelse(
  (hainmueller_immigration$CountryOfOrigin %in% c("India", "Germany", "France", "Mexico", "Philippines", "Poland")) & (hainmueller_immigration$ReasonForApplication %in% c("Seek better job in U.S.", "Reunite with family members already in the U.S."))
, TRUE, FALSE)
hainmueller_immigration$constraint1unconstrained <- ifelse(
  hainmueller_immigration$CountryOfOrigin %in% c("China", "Sudan", "Somalia", "France")
, TRUE, FALSE)
hainmueller_immigration$constraint2constrained <- ifelse(
  (hainmueller_immigration$Job %in% c("Financial analyst", "Computer programmer", "Research scientist", "Doctor")) & (!hainmueller_immigration$Education %in% c("No formal education", "Equivalent to completing fourth grade", "Equivalent to completing eighth grade", "Equivalent to completing high school"))
, TRUE, FALSE)
hainmueller_immigration$constraint2unconstrained <- ifelse(
  hainmueller_immigration$Job %in% c("Janitor", "Waiter", "Child care provider", "Gardener", "Construction worker", "Teacher", "Nurse")
, TRUE, FALSE)
@

@@

<<data_bechtel>>=
if (file.exists("data/bms.rds")) {
    bechtel <- cj_df(rio::import("data/bechtel.rds"))
} else {
	# load original data file
	bechtel <- cj_df(rio::import("data/bechtel_scheve_pnas.dta"))

	# conjoint features
	tmp <- attr(bechtel[["cost_cj"]], "label")
	bechtel[["cost_cj"]] <- rio::factorize(bechtel[["cost_cj"]])
	levels(bechtel[["cost_cj"]]) <- gsub("^.{1}", "€", levels(bechtel$cost_cj))
	attr(bechtel[["cost_cj"]], "label") <- tmp
	rm(tmp)

	tmp <- attr(bechtel[["distrib_cj"]], "label")
	bechtel[["distrib_cj"]] <- rio::factorize(bechtel[["distrib_cj"]])
	attr(bechtel[["distrib_cj"]], "label") <- tmp
	rm(tmp)

	tmp <- attr(bechtel[["ctries_cj"]], "label")
	bechtel[["ctries_cj"]] <- rio::factorize(bechtel[["ctries_cj"]])
	attr(bechtel[["ctries_cj"]], "label") <- tmp
	rm(tmp)

	tmp <- attr(bechtel[["emissions_cj"]], "label")
	bechtel[["emissions_cj"]] <- rio::factorize(bechtel[["emissions_cj"]])
	attr(bechtel[["emissions_cj"]], "label") <- tmp
	rm(tmp)

	tmp <- attr(bechtel[["sanctions_cj"]], "label")
	bechtel[["sanctions_cj"]] <- rio::factorize(bechtel[["sanctions_cj"]])
	levels(bechtel[["sanctions_cj"]])[2:4] <- gsub("^.{1}", "€", levels(bechtel$sanctions_cj)[2:4])
	attr(bechtel[["sanctions_cj"]], "label") <- tmp
	rm(tmp)

	tmp <- attr(bechtel[["monitoring_cj"]], "label")
	bechtel[["monitoring_cj"]] <- rio::factorize(bechtel[["monitoring_cj"]])
	attr(bechtel[["monitoring_cj"]], "label") <- tmp
	rm(tmp)

	tmp <- attr(bechtel[["country"]], "label")
	bechtel[["country"]] <- rio::factorize(bechtel[["country"]])
	attr(bechtel[["country"]], "label") <- tmp
	rm(tmp)

	# covariates
	## environmentalism
	tmp <- attr(bechtel[["support_iec_high_group"]], "label")
	bechtel[["environmentalism"]] <- rio::factorize(bechtel[["support_iec_high_group"]])
	levels(bechtel[["environmentalism"]]) <- paste0("Environmentalism: ", levels(bechtel[["environmentalism"]]))
	attr(bechtel[["environmentalism"]], "label") <- tmp
	rm(tmp)

	## reciprocity
	tmp <- attr(bechtel[["recip_s_high_group"]], "label")
	bechtel[["reciprocity"]] <- rio::factorize(bechtel[["recip_s_high_group"]])
	levels(bechtel[["reciprocity"]]) <- paste0("Reciprocity: ", levels(bechtel[["reciprocity"]]))
	attr(bechtel[["reciprocity"]], "label") <- tmp
	rm(tmp)

    # export
    rio::export(bechtel, "data/bechtel.rds")    
}
@

@@

Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science. While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}. Factorial designs of this sort have a long history but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE). By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline.

While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes: that is, to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning. A positive (negative) AMCE for a given feature can be read as a descriptive measure of high (low) favorability toward profiles with that feature. Though the quantity is causal, it is often read descriptively.

This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity. Such exercises are an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017, EgamiImai2018}. For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups. Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income. In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations. \citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents. \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents. Most of these comparisons are visual or informal. But some involve explicit estimation of the subgroup difference, such as when \citet{KirklandCoppock2017} compare conditional AMCEs across hypothetical partisan and nonpartisan elections. Interpretation of subgroup AMCEs thus involves an implied quantity of interest: the \textit{difference} between two conditional AMCEs.

What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in subgroup differences-in-AMCEs. A difference in effect sizes is distinct from a difference in the preferences so affected. We show that a difference in two (or more) subgroups' favorability toward a conojoint feature --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs in very rare circumstances. As such, no information about the similarity of the subgroups' preferences is provided by comparisons of subgroup AMCEs, yet such comparisons are commonly made in practice.

As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability. Given most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors. \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles. The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.

In what follows, we demonstrate the challenges of conjoint analysis and remind readers of how reference category choice for profile features creates problems for comparing conditional AMCEs across respondent subgroups. We show how the use of an arbitrary reference category means the size, direction, and statistical significance of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features; reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar. We demonstrate this with examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BechtelScheve2013, TeeleKallaRosenbluth2018}). The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (a) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein. Software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout. We conclude with advice for best practices in the analysis and presentation of conjoint results.

@@

Conjoint analysis serves two purposes. One is to assess causal effects. Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, fully randomized conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design. Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features. Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.

Analytically, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved). All quantities of interest relevant to the analysis of conjoint designs therefore derive from combinations of cell means, marginal means, and the grand mean, as in the traditional analysis of factorial experiments. In a forced choice conjoint design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen). \textit{Cell means} are the mean outcome for each particular combination of feature levels. In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved. For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved. While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions. Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.

In fully randomized designs, the average marginal component effects (AMCEs) are simply marginal effects of changing one feature level to another, all else constant. AMCEs therefore depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features. A marginal mean describes the level of favorability toward profiles that have a particular feature level, ignoring all other features. For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany). Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability. If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$. If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one. This constraint on the range of the marginal means also constrains the range of AMCEs. Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018} or \citet{HainmuellerHopkinsYamamoto2014} in their conjoints on candidate choice. In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex. Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.

<<hainmueller_candidate_replication, dependson=c("data_hainmueller_candidate"), fig.height=8, fig.width=10, fig.cap="Replication of Hainmueller et al. (2014) Candidate Experiment using AMCEs and MMs", fig.show="hold", message=FALSE>>=
p1 <- plot(
  cregg::cj(
   hainmueller_candidate, 
   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
   id = ~ resID,
   estimate = "amce"
  ), vline = 0
) + 
  ggplot2::scale_x_continuous(
    limits = c(-0.4, 0.4), 
    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
  ) + 
  ggplot2::geom_text(
    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
 ) + 
 theme(legend.position="none")
p2 <- plot(
  cregg::cj(
   hainmueller_candidate, 
   selected ~ atmilitary + atreligion + ated + atprof + atinc + atrace + atage + atmale,
   id = ~ resID,
   estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none")
gridExtra::grid.arrange(p1, p2, ncol=2)
@

Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation. For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category. This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform. We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of the Hainmueller et al. candidate experiment (left panel) and an analogous examination of the results using marginal means (right panel). Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined). For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively. Similarly, the zero effect size for candidate gender reflects identical marginal means for male and female candidates (0.50 in each case). AMCEs in fully randomized designs are simply differences between marginal means at each feature level and the marginal mean in the reference category, ignoring other features.

The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature. For example, \citet{TeeleKallaRosenbluth2018} summarize their conjoint on public support ``female candidates are favored [over men] by 7.3 percentage points'' (6). Similarly, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of conjoint on preferences toward political candidates:

@@

The most basic thing that can be estimated about the distribution of $Y$ is the expected value, $E[Y]$, or \textit{grand mean} (in the parlance of factorial experiments). We can think of this quantity in terms of the survey implementation process (namely, respondents, tasks, and profiles) or as a simple function of the resulting data:

@@

\section{Bechtel and Scheve (2013) Climate Agreement Experiment}
